Generative Simplex Mapping: Nonlinear Endmember Extraction and Unmixing for Hyperspectral Imagery

### 2024-07-19 paper/paper.tex
Updates from Overleaf

\begin{figure}[H]
\includegraphics[width=\columnwidth]{paper/figures/methods/gsm/gsm-diagram.png}
\caption{Illustration of the GSM. Points in the latent space (green dots) are uniformly distributed at the nodes of a regular grid on the n-simplex whose barycentric coordinates are to be interpreted as the relative abundance of n-many unique sources $z_1, ... z_{N_v}$. Here, $N_v=3$ has been chosen for illustrative purposes. These nodes are mapped into (spectral) data space via the mapping $\psi(z)$ utilizing $M$-many radially symmetric basis functions shown in red. The trained GSM also enables modelling of spectral variability via the precision parameter $\beta$ shown here as a light blue band around the estimated spectra in the data space.\label{fig:gsm-diagram}}
\end{figure}

@@

@@

\section{Results}
\subsection{Linear Mixing}
\subsection{Nonlinear Mixing: Rhodamine Dye Plume}
\subsection{Nonlinear Mixing: Semi-supervised Analysis}

>>>>

\begin{figure}[H]
\includegraphics[width=\columnwidth]{paper/figures/methods/gsm/gsm-diagram.pdf}
\caption{Illustration of the GSM. Points in the latent space (green dots) are uniformly distributed at the nodes of a regular grid on the n-simplex whose barycentric coordinates are to be interpreted as the relative abundance of n-many unique sources $z_1, ... z_{N_v}$. Here, $N_v=3$ has been chosen for illustrative purposes. These nodes are mapped into (spectral) data space via the mapping $\psi(z)$ utilizing $M$-many radially symmetric basis functions shown in red. The trained GSM also enables modelling of spectral variability via the precision parameter $\beta$ shown here as a light blue band around the estimated spectra in the data space.\label{fig:gsm-diagram}}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=0.85\columnwidth]{paper/figures/results-usgs/fit-comparison.pdf}
\caption{Comparison of GSM against NMF on simulated USGS dataset. \label{fig:usgs-fits}}
\end{figure}

@@

\section{Results}
\subsection{Linear Mixing}

\begin{figure}[H]
\includegraphics[width=0.85\columnwidth]{paper/figures/results-usgs/fit-comparison.pdf}
\caption{Comparison of GSM against NMF on simulated USGS dataset. \label{fig:usgs-fits}}
\end{figure}

\subsection{Nonlinear Mixing: Rhodamine Dye Plume}
\subsection{Nonlinear Mixing: Semi-supervised Analysis}
